The Way Forward in Parallelizing Dynamic Languages

### 2014-05-04 talk/icooolps2014/position-paper.tex
change my name, add acks

\authorinfo{Remi Meier}
           {Department of Computer Science\\ ETH Zürich}
           {remi.meier@inf.ethz.ch}
\authorinfo{Armin Rigo}
           {www.pypy.org}
           {arigo@tunes.org}

@@

%% \acks

%% Acknowledgements...

>>>>

\authorinfo{Remigius Meier}
           {Department of Computer Science\\ ETH Zürich}
           {remi.meier@inf.ethz.ch}
\authorinfo{Armin Rigo}
           {www.pypy.org}
           {arigo@tunes.org}

@@

\acks
We would like to thank Maciej Fijalkowski and Carl Friedrich Bolz for
their valuable inputs and the many fruitful discussions.
